\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2012-05-12 doc/USER_MANUAL/manual_SPECFEM3D.tex
fixed NREGIONS

\item [{\texttt{NMATERIALS}}] The number of regions in the mesh.

@@

  \texttt{XI\_begin}  \texttt{XI\_end}  \texttt{ETA\_begin}  \texttt{ETA\_end}  \texttt{material\_ID}

>>>>

\item [{\texttt{NREGIONS}}] The number of regions in the mesh.

@@

  \texttt{NEX\_XI\_BEGIN}  \texttt{NEX\_XI\_END}  \texttt{NEX\_ETA\_BEGIN}  \texttt{NEX\_ETA\_END}  \texttt{NZ\_BEGIN}  \texttt{NZ\_END}  \texttt{material\_ID}
